The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks

### 2024-11-21 paper.Rmd
update

# Define reaction rates
c1 <- (1 - (37 + 2) / 1e6) * 100   # Decay of T2
c2 <- (37 / 1e6) * 100             # Formation of CPD
c3 <- (2 / 1e6) * 100              # Formation of 64-PP

>>>>

# Define reaction rates
c1 <- (1 - (37 + 2) / 1e6) * 100   # No dimerization occurs
c2 <- (37 / 1e6) * 100             # Formation of CPD
c3 <- (2 / 1e6) * 100              # Formation of 64-PP
